# Data sources



The primary data source we used for this project is the Economic Research Service of 
the U.S.Department of Agriculture *[(ERS)*](https://www.usda.gov/). ERS makes estimates
of the milk production costs by using the dairy version of the data from the
Agricultural Resource Management Survey (ARMS).The estimates the ERS made are based both
on the actual data gathered from the ARMS and the estimating models. ERS updated the 
estimates twice a year, one in May and one in October. October released the final version.
The estimates is annual milk cost of production estimates by State and by size of the 
operation. The Milk Cost of Production Estimates data is better used with non-analytical
purposes. More information and background of the data can be found at this 
[*webpage*](https://www.ers.usda.gov/data-products/milk-cost-of-production-estimates/methods/).
All members of our team are responsible for collecting the data. The data is collected by 
directly download the .xlsx file from the official webpage of  the Economic Research Service. 
While we are deciding which dataset is better to illstate our purposes, we also considered 
another data set called [*U.S. Food Imports*](https://www.ers.usda.gov/data-products/us-food-imports/us-food-imports/#All%20tables%20in%20one%20file). There is a dairy section 
in the data set. However, we finally decided that the milk production data can better 
express the milk related problem in the United States rather than the import activity. 
More details about the data set we used for this project are as follows:


## Milk Cost of Production Estimates
This data set was downloaded from the Economic Research Service contains the milk production data of the United States from 2016-2020. The data set has 2900 rows 21 columns.

```{r}
library(janitor)
milkState<- readr::read_csv(here::here("./data/MilkStates2016.csv"))
summary(milkState)
```




```{r, echo=FALSE, results='asis'}
milkState<- readr::read_csv(here::here("./data/MilkStates2016.csv"))
knitr::kable(milkState[c(1,406,712,2126,2451,2866),c(6,11,15:16,18) ], caption = "Major variables used",
             row.names = F,font_size = 10)
```
These are the major variables used for this project.
Item2: listed the categories of cost or revenue activities.
Region: states of the United States
Year: the record year
Value: the amount of money, corresponds to the categories of Item2


Issues with this data set: 

Even though this data set is well organized. It still has some issues.

1. The data value is not accurate enough to be used for analysis purposes.By reading the data 
set background on Economic Research Service's official website, it is easier to find that some 
amount of the data is estimated by using actual data and model. It makes sense that it is 
difficult to ask and gather milk production and seeling data from farmers, because it requires
lots of work, and farmers may even do not know exactly how much they paid or gained in the milk 
production industry.

2. The data set only covers milk production data of 19 States of the United States. It could be 
that the amount of milk production and seeling can be ignored compared to these 19 States. 
However, it is imappropreate to just treat the milk production of the other States as 
"NO MILK PRODUCED" at all. 


## Other Minor Date Set used
1. name.tsv
name.tsv is a flie about the States names and their abbreviations of the United States. This data is found online from [*this website*](https://gist.github.com/lbui30/65c2707e615841efaf35959aedac8ca9). The original name of the data set is called "us-state-names.tsv". We used this data set to draw the interactive map of the six section.A sample of the data is listed below:
(the data set has 60 rows 3 columns)
```{r, echo=FALSE, results='asis'}
names<- readr::read_tsv(here::here("data/name.tsv"))
knitr::kable(names[c(1,2,3), ], caption = "State Names",
             row.names = F,font_size = 10)
```


Issues with this data set:

*The number of States in the United States are too much for us, since we only need to consider some of the States. 




2. state.json
state is a flie about the geological information of the States in the United States. This data is found online 
from [*this website*](https://gist.github.com/lbui30/65c2707e615841efaf35959aedac8ca9). The original name of 
the data set is called "states-10m.json". We used this data set to draw the interactive map of the six 
section as well. The json file is too large to be shown here that you can find it in our github 
[*here*](https://github.com/yajiez11/Milk_Analysis/blob/main/data/state.json).




Issues with this data set:

*The number inside this data set includes too much geological numbers to be shown in R, and many of the data is not useful. 
