# Data sources



The primary data source we used for this project is the Economic Research Service of 
the U.S.Department of Agriculture *[(ERS)*](https://www.usda.gov/). ERS makes estimates
of the milk production costs by using the dairy version of the data from the
Agricultural Resource Management Survey (ARMS).The estimates the ERS made are based both
on the actual data gathered from the ARMS and the estimating models. ERS updated the 
estimates twice a year, one in May and one in October. October released the final version.
The estimates is annual milk cost of production estimates by State and by size of the 
operation. The Milk Cost of Production Estimates data is better used with non-analytical
purposes. More information and background of the data can be found at this 
[*webpage*](https://www.ers.usda.gov/data-products/milk-cost-of-production-estimates/methods/).
All members of our team are responsible for collecting the data. The data is collected by 
directly download the .xlsx file from the official webpage of  the Economic Research Service. 
While we are deciding which dataset is better to illstate our purposes, we also considered 
another data set called [*U.S. Food Imports*](https://www.ers.usda.gov/data-products/us-food-imports/us-food-imports/#All%20tables%20in%20one%20file). There is a dairy section 
in the data set. However, we finally decided that the milk production data can better 
express the milk related problem in the United States rather than the import activity. 
More details about the data set we used for this project are as follows:


## Milk Cost of Production Estimates
This data set was downloaded from the Economic Research Service contains the milk production data of the United States from 2016-2020.

```{r}
milkState<- readr::read_csv(here::here("./data/MilkStates2016.csv"))
summary(milkState)
```




```{r, echo=FALSE, results='asis'}
milkState<- readr::read_csv(here::here("./data/MilkStates2016.csv"))
knitr::kable(milkState[c(1,406,712,2126,2451,2866),c(6,11,15:16,18) ], caption = "Major variables used",
             row.names = F,font_size = 10)
```
These are the major variables used for this project.
Item2: listed the categories of cost or revenue activities.
Region: states of the United States
Year: the record year
Value: the amount of money, corresponds to the categories of Item2


***Issues with this data set: ***

