# Data transformation






## Data Transformation for Interactive Plot
Only used columns Region, Year and Value for the Total, gross value of production for the 
interactive plots in section 6. This data file is called totalRevenue.csv
```{r}
library(tidyverse)
milkStates <- read.csv(file = 'data/MilkStates2016.csv')
milkStates <- milkStates%>%
  filter(ItemId==380)
milkStates <- milkStates[,c(11,15,16)]
knitr::kable(milkStates[c(1:7), ], caption = "Variable Used for Interactive Plot",
             row.names = F,font_size = 10)

```



Changed the TotalRevenue.csv a little bit by using pivot_wider, so it is easier to use in 
the interactive plot section. This data file is called totalRevenue_n.csv
```{r}
milkStates <- read.csv(file = 'data/MilkStates2016.csv')
milkStates <- milkStates%>%
  filter(ItemId==380)
milkStates <- milkStates[,c(11,15,16)]
milkNew <- milkStates %>%
  pivot_wider(id_cols = c(Region,Year),names_from = Year,values_from = Value) %>%
  rowwise()
knitr::kable(milkNew[c(1,2), ], caption = "Pivot Wider version of totalRevenue.csv",
             row.names = F,font_size = 10)
```

